Title

### 2019-05-10 paper_notes.Rmd
finalized simulation, check

@@

f0t8 <- f(0.5,0.6,0,8)
f1t8 <- f(0.5,0.6,1,8)
f2t8 <- f(0.5,0.6,2,8)
f3t8 <- f(0.5,0.6,3,8)
f4t8 <- f(0.5,0.6,4,8)
f5t8 <- f(0.5,0.6,5,8)
f6t8 <- f(0.5,0.6,6,8)
f7t8 <- f(0.5,0.6,7,8)
f8t8 <- f(0.5,0.6,8,8)

>>>>

Test for $utility = 1$, utility = 0 means that agents want $0%$ similars in their neighbborhood, thus neighborhoods with not any similar one will have max utility and literally decreasing for neighborhoods with more similar ones. With $\beta = 0$, agents don't care about the composition of the neighborhood, so that both current location and alternative patch have prob. equal to zero, selecting alternative or current one randomly, sometimes relocating. Increasing $\beta$, the utility attributed to the patch due to neighborhood composition is multiplied times $\beta$, meaning those neighborhoods less inhabited by similar ones will higher probability to be chosen, thus increasing integration. It is not agents don't care, but agents care that similar ones are not there. See if this is related to @bruch2006's error cited by @van2009

@@

f0t8 <- f(0,0.6,0,8)
f1t8 <- f(0,0.6,1,8)
f2t8 <- f(0,0.6,2,8)
f3t8 <- f(0,0.6,3,8)
f4t8 <- f(0,0.6,4,8)
f5t8 <- f(0,0.6,5,8)
f6t8 <- f(0,0.6,6,8)
f7t8 <- f(0,0.6,7,8)
f8t8 <- f(0,0.6,8,8)
